### 2021-11-25 sections/awards.tex
Update awards.tex

\begin{cvhonors}
\cvhonor
{St Hilda's College Travel and Book Grants} 
{Allowances for conference participation in Portugal and books (travel grant was declined because of coronavirus pandemic), {\pounds} 745} 
{Oxford, UK}
{2020}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{FONDECYT Thesis Writing Grant}
{Financial support for MA field work (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), {\pounds} 1,150}
{Santiago, Chile}
{2012}
\end{cvhonors}

>>>>

\begin{cvhonors}
\cvhonor
{St Hilda's College Travel and Book Grants} 
{Allowances for conference participation in Portugal and books, {\pounds} 745} 
{Oxford, UK}
{2020}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{FONDECYT Thesis Writing Grant}
{Financial support for MA fieldwork (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), {\pounds} 1,150}
{Santiago, Chile}
{2012}
\end{cvhonors}
